Andres Karjus

### 2021-10-28 index.Rmd
news

* Andres Karjus, Richard A. Blythe, Simon Kirby, Tianyu Wang, Kenny Smith. 2021. Conceptual similarity and communicative need shape colexification". [Cognitive Science](https://doi.org/10.1111/cogs.13035) | [pdf](https://andreskarjus.github.io/papers/Karjus_2021__Conceptual_Similarity_and_Communicative_Need_Shape_Colexification_An_Experimental_Study__Cognitive_Science.pdf) |  [bib](https://andreskarjus.github.io/bib/karjus_2021_cogsci.bib) | [preprint](arxiv.org/abs/2103.11024) | [code and data](https://github.com/andreskarjus/colexification_experiment)
* Andres Karjus, 2020. Competition, selection and communicative need in language change. PhD thesis, University of Edinburgh | [pdf](https://andreskarjus.github.io/thesis/Andres_Karjus_phd_thesis.pdf) | [1-page non-technical summary](https://andreskarjus.github.io/thesis/english_summary.pdf) | [eestikeelne lühikokkuvõte](https://andreskarjus.github.io/thesis/doktoritoo_ylevaade_AK.pdf)
*  Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Communicative need modulates competition in language change | [preprint](https://arxiv.org/abs/2006.09277)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Challenges in detecting evolutionary forces in language change using diachronic corpora. Glossa: a journal of general linguistics, 5(1), p.45. | [open access](http://doi.org/10.5334/gjgl.909) | [code](https://github.com/andreskarjus/wfsim_fit)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2020. Quantifying the dynamics of topical fluctuations in language. Language Dynamics and Change 10(1), 86-125 | [open access](https://doi.org/10.1163/22105832-01001200) | [code](https://github.com/andreskarjus/topical_cultural_advection_model)
* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [journal link](https://doi.org/10.1163/22105832-00802004) | [open postprint](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | sociolinguistic [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract, full paper above] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [journal link](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>

@@

-  [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_

>>>>

* Andres Karjus, Richard A. Blythe, Simon Kirby, Tianyu Wang, Kenny Smith. 2021. Conceptual similarity and communicative need shape colexification". [Cognitive Science](https://doi.org/10.1111/cogs.13035) | [pdf](https://andreskarjus.github.io/papers/Karjus_2021__Conceptual_Similarity_and_Communicative_Need_Shape_Colexification_An_Experimental_Study__Cognitive_Science.pdf) |  [bib](https://andreskarjus.github.io/bib/karjus_2021_cogsci.bib) | [code and data](https://github.com/andreskarjus/colexification_experiment)
* Andres Karjus, 2020. Competition, selection and communicative need in language change. PhD thesis, University of Edinburgh | [pdf](https://andreskarjus.github.io/thesis/Andres_Karjus_phd_thesis.pdf) | [1-page non-technical summary](https://andreskarjus.github.io/thesis/english_summary.pdf) | [eestikeelne lühikokkuvõte](https://andreskarjus.github.io/thesis/doktoritoo_ylevaade_AK.pdf)
*  Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Communicative need modulates competition in language change | [preprint](https://arxiv.org/abs/2006.09277)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Challenges in detecting evolutionary forces in language change using diachronic corpora. Glossa: a journal of general linguistics, 5(1), p.45. | [open access](http://doi.org/10.5334/gjgl.909) | [code](https://github.com/andreskarjus/wfsim_fit)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2020. Quantifying the dynamics of topical fluctuations in language. Language Dynamics and Change 10(1), 86-125 | [open access](https://doi.org/10.1163/22105832-01001200) | [code](https://github.com/andreskarjus/topical_cultural_advection_model)
* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [journal link](https://doi.org/10.1163/22105832-00802004) | [open postprint](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | sociolinguistic [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract, full paper above] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [journal link](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>

@@

- [Conference on Complex Systems 2021](https://ccs2021.univ-lyon1.fr/) (October 2021) | [slides](https://andreskarjus.github.io/talks/ccs2021/Karjus_CCS2021_Capturing_aesthetic_complexity.pdf)
- [Protolang 7](https://blogs.phil.hhu.de/protolang7/programme/) (September 2021) | [slides](https://andreskarjus.github.io/slides/andres_karjus_protolang7.pdf)
- [TÜling](https://www.keel.ut.ee/et/tuling) (April 2021)
- [Colloquium for Computational Linguistics and Linguistics in Stuttgart](https://www.ims.uni-stuttgart.de/en/research/colloquium/) | [Slides](https://andreskarjus.github.io/talks/stuttgart2021/andres_karjus_lexical_dynamics_slides_stuttgart2021.pdf) | [Recording](https://www.ims.uni-stuttgart.de/documents/aktuelles/veranstaltungen/210111-Karjus-Talk-Colloq-Recording.mp4)
- [RUSE 2019](http://rusesymposium.org.uk/). Slides [here](https://andreskarjus.github.io/ruse2019).
- [CL2019](http://www.cl2019.org/). Slides [here](https://andreskarjus.github.io/cl2019talk.html).
- [Culture Conference 2019](https://culture-conference.com/programme-2019/), Poster [here](https://andreskarjus.github.io/lexcom_poster).
- [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html) | _Modelling lexical interactions in diachronic corpora_ |  [poster](https://andreskarjus.github.io/isle_poster)
- University of Edinburgh [Centre for Language Evolution](http://www.lel.ed.ac.uk/cle/) seminar series | _Challenges in detecting evolutionary forces in language change using diachronic corpora_ | [slides](https://andreskarjus.github.io/evoforces_cletalk/slides.html) | [code](https://github.com/andreskarjus/wfsim_fit)
- Corpus Linguistics in Scotland Network Meeting, _Topical Fluctuations and Lexical Interactions in Diachronic Corpora_
